InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-02-06 paper.tex
Update paper.tex
Co-authored-by: Max Buchholz <Max.Buchholz@gmx.de>

Another AI generated image detector model is \textbf{Is It AI?} developed by Is It AI. The tool first determines different features of the image, e.g. colour patterns, shapes and textures. These features are determined using machine learning models. Afterwards, the patterns are compared to those, typically contained in human- or AI-generated content. The Is It AI-model was trained on large datasets of human- and AI-generated content to receive the base patterns to compare to. The tool is freely usable through an web interface. \cite{IsItAI2024}

There is also an AI-generated-image-detection-approach from Content at Scale. They published their \textbf{Advanced AI Image Detector} as a free web tool to detect generated AI images. The application categorizes the input content by evaluating pixels, smoothness and other AI image patterns. \cite{ContentAtScale2024Advanced}

@@

>>>>

@@

For the ease of use and low time consumption we implemented a simple python command line interface, that makes it easy to define a pipeline consisting of a generator, processor and evaluator. It is also possible to enter multiple processors for one pipeline, to stack and apply them together on the content.

The resulting pipelines, especially for the images, were very resource intensive and could not be run efficiently on our own machines. We chose to use the free Google Colab resources, consisting of a NVIDIA Tesla T4 GPU that would speed up the pipelines up to 40x compared to our local execution time and allowed to have the same environment for all experiments.
